---
title: "Update Errors"
output:
  html_document:
    theme: paper
    toc: true
    toc_float: true
---

This page displays any  mismatches in data between the current cohort file and survey inputs. Not every mismatch is an error that needs to be corrected.

**No changes have been made, and the cohort file has been archived for safety.**

Next steps:

1. Review all tables on this page.
2. Where needed, make changes to your source or to [Editor](Consent/Editor.csv "Click to open Editor").
3. Re-run `update()`.
4. Once you are satisfied that *all* the items remaining on this page are intended, run `update_confirm()`.

# Changes from data

These changes are from your data source, `r cat(cluster_cfg$setup_get$get)`.

```{r, echo = FALSE, results = "asis"}
for(i in 1:length(coh_src_errs)){
  cat(paste0(
    "## ",
    names(coh_src_errs)[i],
    "\n\n"
  ))
  knitr::kable(coh_src_errs[[i]])
  cat("\n\n")
}
```


# Manual changes

These changes are from Editor and, when in conflict, will override changes from your data source.

```{r, echo = FALSE, results = "asis"}
for(i in 1:length(coh_man_errs)){
  cat(paste0(
    "## ",
    names(coh_man_errs)[i],
    "\n\n"
  ))
  knitr::kable(coh_man_errs[[i]])
  cat("\n\n")
}
```

